---
title: "Report for federal government"
author: MayunkB
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
    keep_tex: true
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: plainnat
subtitle: "Machine learning consultancy"
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---


```{r , echo = FALSE, message = FALSE, warning = FALSE}

library(knitr)
library(kableExtra)
```



\clearpage

# Section 1





This is a new version report


Table example using R:

```{r tableexample, echo = FALSE}
dt <- mtcars[1:5, 1:6]

kable(dt, caption = "Table example") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```




\clearpage

# Section 2


Table example using latex: 

\begin{table}
\begin{center}
  \begin{tabular}{ l | c | r }
    \hline
    1 & 2 & 3 \\ \hline
    4 & 5 & 6 \\ \hline
    7 & 8 & 9 \\
    \hline
  \end{tabular}
  \caption{This is my table using latex} \label{tab:sometab}
\end{center}
\end{table}


Example from \href{Wiki}{https://en.wikibooks.org/wiki/LaTeX/Tables}


\clearpage

# Section 3

blah blah balh


\clearpage

# Section 4




\clearpage

# Citation examples

[More styles for natbib here](https://www.overleaf.com/learn/latex/Natbib_bibliography_styles)


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2
